### 2016-07-12 capability-machine.tex
removed two conditions from obs. rel.

The ticket dispenser test program uses $\malloc$. To be able to reason about programs that use $\malloc$, we assume that it follows the following specification. If you provide it with one argument, namely the size of the allocation you wish and a return capability, then at some point $\pcreg$ will contain an executable capability based on this return capability and the return register will contain a $\rwx$ capability for the freshly allocated memory. 
\begin{specification}[Malloc v.2]
  \begin{align*}
    &\forall \Phi \in \Mems \ldotp \forall \hsfoot, \hsframe \in \HeapSegments\ldotp\\
    &\quad \forall n, i, \size \in \nats\ldotp\forall b,e,a,m_b,m_e\in \Addrs\ldotp\forall p \in \Perms \ldotp\\
    &\qquad W_{\malloc} = [i \mapsto \iota_{\malloc}] \land \\
    &\qquad \dom(\hsfoot) = [m_b,m_e] \land \\
    &\qquad \memheap = \hsfoot \uplus \hsframe \land\\
    &\qquad \heapSat[\hsfoot]{n}{W_{\malloc}} \land \\
    &\qquad \memreg(r_1) = \size \land \\
    &\qquad \size \geq 0 \land \\
    &\qquad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \memreg(\pcreg) = (\entry,m_b,m_e,m_b) \\
    &\qquad\Rightarrow \\
    &\qquad \quad\exists \Phi' \in \Mems \ldotp \exists \hsfoot', \hsframe' \in \HeapSegments\ldotp\\
    &\qquad \qquad \exists j,k \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \\
    &\qquad \qquad \quad \Phi \step[j]\Phi' \land \\
    &\qquad \qquad \quad \memheap[\Phi']=\hsfoot' \uplus \hsframe' \land\\
    &\qquad \qquad \quad W' = [i \mapsto \iota_{\malloc}, k \mapsto \iota^0_{b',e'}] \land \\
    &\qquad \qquad \quad \heapSat[\hsfoot']{n-j}{W'} \land \\
    &\qquad \qquad \quad \memreg[\Phi'](\pcreg) = (\updatePcPerm{p},b,e,a) \land \\
    &\qquad \qquad \quad \memreg[\Phi'](r_1) = (\rwx,b',e',b') \land \\
    &\qquad \qquad \quad \forall r \in \RegName \setminus \{\pcreg,r_1\} \ldotp \memreg[\Phi'](r) = 0
\end{align*}
\end{specification}
\lau{I am not satisfied with the pc in the premise.}

@@

If we start running in $\Phi$ until $\memreg(\pcreg)$ points to $\jmp{\malloc}$, then the configuration is the same as $\Phi$ except:
\begin{itemize}
\item $\memheap(0)$ contains $-1$
\item the io capability is saved to the designated address in the tdtp
\item $r_1$ contains the size of the ticket dispenser program (9)
\item $r_0$ contains the return capability $(\rwx,\initb,\inite, \retm)$
\end{itemize}
Call this new heap $\Phi'$

@@

Consider what the ``good observations'' should be? Before we do that - what should the end result of a computation be?
\begin{align*}
  \observations \quad : & \quad  \Worlds \monfun \UPred{\Confs} \\
  \observations (W) \defeq & \{ \npair{(\reg,\heap)} \mid \\
                           & \quad (\exists \reg', \heap' \ldotp (\reg,\heap) \step[n] (\reg',\heap')) \lor \\ %Define the step stuff 
                           & \quad (\exists i \leq n \ldotp (\reg,\heap) \step[i] \failed) \lor \\
                           & \quad (\forall \heap', i \leq n \ldotp (\reg,\heap) \step[i] (\halted,\heap')  \\
                           & \qquad \Rightarrow \exists \heap'', \heap_f \ldotp \heap' = \heap'' \uplus \heap_f \land \heapSat[heap'']{n-i}{W}
\end{align*}
Removed the condition $\npair[n-i]{\heap'(0)} \in \stdvr(W)$.\\

>>>>

The ticket dispenser test program uses $\malloc$. To be able to reason about programs that use $\malloc$, we assume that it follows the following specification. If you provide it with one argument, namely the size of the allocation you wish and a return capability, then at some point $\pcreg$ will contain an executable capability based on this return capability and the return register will contain a $\rwx$ capability for the freshly allocated memory. 
\begin{specification}[Malloc v.2]
  \begin{align*}
    &\forall \Phi \in \Mems \ldotp \forall \hsfoot, \hsframe \in \HeapSegments\ldotp\\
    &\quad \forall n, i, \size \in \nats\ldotp\forall b,e,a,m_b,m_e\in \Addrs\ldotp\forall p \in \Perms \ldotp\\
    &\qquad W_{\malloc} = [i \mapsto \iota_{\malloc}] \land \\
    &\qquad \dom(\hsfoot) = [m_b,m_e] \land \\
    &\qquad \memheap = \hsfoot \uplus \hsframe \land\\
    &\qquad \heapSat[\hsfoot]{n}{W_{\malloc}} \land \\
    &\qquad \memreg(r_1) = \size \land \\
    &\qquad \size \geq 0 \land \\
    &\qquad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \memreg(\pcreg) = (\entry,m_b,m_e,m_b) \\
    &\qquad\Rightarrow \\
    &\qquad \quad\exists \Phi' \in \Mems \ldotp \exists \hsfoot', \hsframe' \in \HeapSegments\ldotp\\
    &\qquad \qquad \exists j,k \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \\
    &\qquad \qquad \quad \Phi \step[j]\Phi' \land \\
    &\qquad \qquad \quad \memheap[\Phi']=\hsfoot' \uplus \hsframe' \land\\
    &\qquad \qquad \quad W' = [i \mapsto \iota_{\malloc}, k \mapsto \iota^0_{b',e'}] \land \\
    &\qquad \qquad \quad \heapSat[\hsfoot']{n-j}{W'} \land \\
    &\qquad \qquad \quad \memreg[\Phi'](\pcreg) = (\updatePcPerm{p},b,e,a) \land \\
    &\qquad \qquad \quad \memreg[\Phi'](r_1) = (\rwx,b',e',b') \land \\
    &\qquad \qquad \quad \forall r \in \RegName \setminus \{\pcreg,r_1\} \ldotp \memreg[\Phi'](r) = 0
\end{align*}
\end{specification}
\lau{I am not satisfied with the pc in the premise. The exact capability necessary very much depent on the implementation (this is mostly a note to myself.)}

@@

If we start running in $\Phi$ until $\jmp{\malloc}$ has just been executed, then the configuration is the same as $\Phi$ except:
\begin{itemize}
\item $\memheap(0)$ contains $-1$
\item the io capability is saved to the designated address in the tdtp
\item $r_1$ contains the size of the ticket dispenser program (9)
\item $r_0$ contains the return capability $(\rwx,\initb,\inite, \retm)$
\end{itemize}
Call this new heap $\Phi'$

@@

Consider what the ``good observations'' should be? Before we do that - what should the end result of a computation be?
\begin{align*}
  \observations \quad : & \quad  \Worlds \monfun \UPred{\Confs} \\
  \observations (W) \defeq & \{ \npair{(\reg,\heap)} \mid \\
                           & \quad (\forall \heap', i \leq n \ldotp (\reg,\heap) \step[i] (\halted,\heap')  \\
                           & \qquad \Rightarrow \exists \heap'', \heap_f \ldotp \heap' = \heap'' \uplus \heap_f \land \heapSat[heap'']{n-i}{W}
\end{align*}
Removed the condition $\npair[n-i]{\heap'(0)} \in \stdvr(W)$.\\
